The Noisy Work of Uncertainty Visualisation Research: A Review

### 2024-07-24 paper.qmd
started moving stuff around

### Value Supressing Uncertainty Palettes
### There is no such thing as a test for everything
As we move through these methods, it seems that the validity of any overarching insight becomes more visible at the cost of our ability to extract particular values of signal or noise. Therefore, given that the primary goal of visualisation *is* insights [@North2006], visualisation authors should err on the side of representing suppressed signal as a single variable, rather than visualising uncertainty separately using two different channels.

@@

# Implicitly Combining Uncertainty and Signal
## Pixel maps
## Show me the data

@@

# MAPS

```{r}
#| echo: false
#| message: false
#| warning: false
#| eval: false

# Display plots and palettes
p3a
p3b
show_col(VSUP, ncol=8, labels=FALSE)
p4a
p4b
show_col(basecols, ncol=8, labels=FALSE)
```

>>>>

### Value Supressing Uncertainty Palettes

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-vsup
#| fig-cap: "A map made with a VSUP. The counties of Iowa are coloured acording to it's average daily temperature and the variance in temperature, although the space they have been mapped to is slightly warped."
#| fig-subcap: 
#|   - "High Variance Data"
#|   - "Low Variance Data"
#|   - "VSUP Palette"
#| layout-ncol: 3
#| layout-valign: "bottom"

p3a
p3b
show_col(VSUP, ncol=8, labels=FALSE)

### There is no such thing as a test for everything
As we move through these methods, it seems that the validity of any overarching insight becomes more visible at the cost of our ability to extract particular values of signal or noise. Therefore, given that the primary goal of visualisation *is* insights [@North2006], visualisation authors should err on the side of representing suppressed signal as a single variable, rather than visualising uncertainty separately using two different channels.

@@

# Implicitly Combining Uncertainty and Signal
## Pixel maps
```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-pixel
#| fig-cap: "A pixel map of the counties of Iowa. In this map, each county is broken up into several smaller regions and coloured according to a potential daily temperature, given the its average daily temperature and its sampling distribution. This results in each county being represented by a sample rather than a single value."
#| fig-subcap: 
#|   - "High Variance Data"
#|   - "Low Variance Data"
#|   - "Pixel Map Palette"
#| layout-ncol: 3
#| layout-valign: "bottom"

# Display plots and palettes
p4a
p4b
show_col(basecols, ncol=8, labels=FALSE)

```
## Show me the data

@@
